Handbook streamFind: Backend

### 2024-07-31 README.Rmd
Updated website

The StreamFind project, entitled "Flexible data analysis and workflow designer to identify chemicals in the water cycle", is funded by the [Bundesministerium für Bildung und Forschung (BMBF)](https://www.bmbf.de) and is a cooperation between the [Institut für Umwelt & Energie, Technik & Analytik e. V. (IUTA)](https://www.iuta.de), the [Forschungszentrum Informatik (FZI)](https://www.fzi.de/) and supporting partners. The goal of the StreamFind project is the development and assembly of data processing workflows for mass spectrometry and spectroscopy and the application of the workflows in environmental and quality studies of the water cycle. The StreamFind aims to stimulate the use of advanced data analysis (e.g., non-target screening, statistical analysis, etc.) in routine studies, promoting standardization of data processing and structure and easing the retrospective evaluation of data. The StreamFind platform is directed to academics but also technicians, due to the aspired comprehensive documentation, well categorized set of integrated modular functions and the graphical user interface.  
<br>
The library of [StreamFind](https://github.com/odea-project/StreamFind) is an R package (this repository). The graphical user interface (GUI) is a Web App developed in JavaScript and can be found in the [StreamFind-App](https://github.com/odea-project/StreamFind-App) repository. The StreamFind development is ongoing, please [contact us](mailto:cunha@iuta.de) for questions  or collaboration.

@@

For installation of the StreamFind R package, it is recommended to first install the dependencies. Besides [R](https://cran.r-project.org/) and [RTools](https://cran.r-project.org/bin/windows/Rtools/) (the latter is only recommended for Windows users), the StreamFind depends on the [patRoon](https://github.com/rickhelmus/patRoon) R package and its dependencies. The patRoon R package combines several tools for basic and advanced data processing and can be used interchangeably with the StreamFind R package. Installation instructions for patRoon and its dependencies can be found [here](https://rickhelmus.github.io/patRoon/handbook_bd/manual-installation.html#r-prerequisites).

Then, the StreamFind R package can be installed from the GitHub repository.

```{r install-streamfind, eval=FALSE}
remotes::install_github("odea-project/StreamFind", dependencies = TRUE)
```

The supplementary [StreamFindData](https://github.com/odea-project/StreamFindData) R package holds the data used in examples and other documentation assets of the StreamFind R package and can also be installed from the GitHub repository.

```{r install-streamfinddata, eval=FALSE}
remotes::install_github("odea-project/StreamFindData")
```

@@

The documentation and usage examples of the StreamFind R package can be found in the [reference page](https://odea-project.github.io/StreamFind/reference/index.html) and [articles](https://odea-project.github.io/StreamFind/articles/index.html) of the [webpage](https://odea-project.github.io/StreamFind/index.html).

>>>>

The StreamFind is developed under the project ["Flexible data analysis and workflow designer to identify chemicals in the water cycle"](https://www.bildung-forschung.digital/digitalezukunft/de/wissen/Datenkompetenzen/datenkompetenzen_wissenschaftlichen_nachwuchs/Projekte/stream_find.html) which is funded by the [Bundesministerium für Bildung und Forschung (BMBF)](https://www.bmbf.de). The development is conducted by the [Institut für Umwelt & Energie, Technik & Analytik e. V. (IUTA)](https://www.iuta.de), the [Forschungszentrum Informatik (FZI)](https://www.fzi.de/) and supporting partners. The goal of the StreamFind is the development and assembly of data processing workflows for different types of analytical data (e.g., mass spectrometry and spectroscopy) and the application of the workflows in diverse fields (e.g., environmental and quality studies of the water cycle). The StreamFind aims to stimulate the use of advanced data analysis (e.g., non-target screening, statistical analysis, etc.) in routine studies, promoting standardization of data structure and processing and easing the retrospective evaluation of data. The StreamFind platform is directed to academics but also technicians, due to the aspired comprehensive documentation, well categorized set of integrated modular functions and the embedded shiny graphical user interface.  
<br>
The StreamFind development is ongoing, please [contact us](mailto:cunha@iuta.de) for questions  or collaboration.

@@

Assuming that the [R](https://cran.r-project.org/) software is installed, the StreamFind R package can be installed from the GitHub repository via the [BiocManager](https://www.bioconductor.org/install/).

```{r install-streamfind, eval=FALSE}
if (!require("BiocManager", quietly = TRUE))
  install.packages("BiocManager")
BiocManager::install("odea-project/StreamFind", dependencies = TRUE)
```

<!-- For installation of the StreamFind R package, it is recommended to first install the dependencies. Besides [R](https://cran.r-project.org/) and [RTools](https://cran.r-project.org/bin/windows/Rtools/) (the latter is only applicable for Windows users), the StreamFind depends on the [patRoon](https://github.com/rickhelmus/patRoon) R package and its dependencies. The patRoon R package combines several tools for basic and advanced data processing and can be used interchangeably with the StreamFind R package. Installation instructions for patRoon and its dependencies can be found [here](https://rickhelmus.github.io/patRoon/handbook_bd/manual-installation.html#r-prerequisites). -->

<!-- Then, the StreamFind R package can be installed from the GitHub repository. -->

```{r install-streamfind, eval=FALSE}
#remotes::install_github("odea-project/StreamFind", dependencies = TRUE)
```

<!-- The supplementary [StreamFindData](https://github.com/odea-project/StreamFindData) R package holds the data used in examples and other documentation assets of the StreamFind R package and can also be installed from the GitHub repository. -->

```{r install-streamfinddata, eval=FALSE}
#remotes::install_github("odea-project/StreamFindData")
```

@@

The documentation and usage examples of the StreamFind R package can be found in the [reference page](https://odea-project.github.io/StreamFind/reference/index.html) and [articles](https://odea-project.github.io/StreamFind/articles/index.html) of the [webpage](https://odea-project.github.io/StreamFind/index.html), respectively.
